---
title: "Introductions"
author: "Carl Kenneth Martin"
date: "1/27/2020"
output: html_document
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### 1 Major & Classes
  Major: Computer Science and Engineering  
  Class Difficulty Ranking:
  
      1. ENGR 057 - Statics and Dynamics  
      2. MATH 032 - Probability and Statistics
      3. MATH 024 - Linear Algebra

##### 2 Why Math 32?
I am enrolled in this class becuase i find statstics and probabilty to be somewhat interesting. What I hope to learn from this class is a deeper insight and understand of how statistics is applied in everyday scenarios.

##### 3 Fascinating Fact
```{r}
knitr::opts_chunk$set(echo = TRUE)

#"Alchohol" in alcholic beverages like beer, wine, and spirits is actually ethanol (ethyl alcohol). It is actually the only type of alcohol you can drink without doing serious damage to your body.
```

##### 4 Hope and Goals
* Graduate college with a BS in Computer Science and Engineering
* I hope to one day go sky diving.

##### 5 Fears and Obstacles
```{r}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
# I have a fear of heights and an obstacle I have to face is my balcony at my house every morning.
```

##### 6 Lively Song 
*ACDC - Back in Black*