---
title: "Exploration 2"
author: "Kenneth Martin"
date: "1/26/2020"
output: 
  html_document:
        theme: cerulean
---

# Math 32
## Exploration 2

In this `exploration`, you are asked to

* find sample means and medians from a randomized data sample
* observe the differences in the practice of using means or medians

1. First,
    a. Type your name into the author field in the YAML parameters above
    b. Also save this file while replacing "template" with your full name (be sure to keep the *.rmd file format).

2. Demonstrate your understanding about the example code block below by adding at least 5 comments in the code block in your own words.

```{r, message = FALSE, warning = FALSE}
library("ggplot2")

N <- 32 # Sample Size

shoe_sizes <- 6:14 # Set boundaries from 6 to 14
without_outlier <- sample(shoe_sizes, N, replace = TRUE) # Take a sample with replacement 
df_without_outlier <- data.frame(without_outlier) # Create dataframe

outlier <- 100 # init outlier value to 100
with_outlier <- c(without_outlier, outlier)
df_with_outlier <- data.frame(with_outlier)

ggplot(df_without_outlier, aes(x = without_outlier)) +
  geom_histogram(binwidth = 1, color = "black", fill = "white") +
  geom_vline(aes(xintercept = mean(without_outlier)),
             color = "blue", linetype = "dashed", size = 2) +
  labs(title = "Shoe Sizes", subtitle = "Exploring Means",
       caption = "Math 32", x = "shoe sizes") +
  theme_minimal() +
  theme(legend.position = "none")
```

3. Make at least two observations about the results (the graph) in an unordered list.
* The graph seems normal and is not skewed.
* The mean does not match the median.

4. In the code block below,

    a. set the `eval` parameter for the code block to `TRUE`
    b. graph the "with outlier" data by making changes in the `ggplot` line
    c. *add* another `geom_vline` layer that 
        * calculates and displays the mean with the outlier
        * has a red color
        * is a dotted line
    d. replace "Math 32" with your name in the caption
  
```{r, eval = TRUE}
ggplot(df_with_outlier, aes(x = with_outlier)) +
  geom_histogram(binwidth = 1, color = "black", fill = "white") +
  geom_vline(aes(xintercept = mean(without_outlier)),
             color = "blue", linetype = "dashed", size = 2) +
  geom_vline(aes(xintercept = mean(with_outlier)),
             color = "red", linetype = "dotted", size = 2) +
  labs(title = "Shoe Sizes", subtitle = "Exploring Means",
       caption = "Kenneth Martin", x = "shoe sizes") +
  theme_minimal() +
  theme(legend.position = "none")
```

5. Repeat the previous task in a new code block, but compute the `median` without and with the outlier.

```{r, eval = TRUE}
ggplot(df_with_outlier, aes(x = with_outlier)) +
  geom_histogram(binwidth = 1, color = "black", fill = "white") +
  geom_vline(aes(xintercept = median(without_outlier)),
             color = "blue", linetype = "dashed", size = 2) +
  geom_vline(aes(xintercept = median(with_outlier)),
             color = "red", linetype = "dotted", size = 2) +
  labs(title = "Shoe Sizes", subtitle = "Exploring Means",
       caption = "Kenneth Martin", x = "shoe sizes") +
  theme_minimal() +
  theme(legend.position = "none")
```
6.  Compute the *difference* between the means from before and after including the outlier.  Compute the *difference* between the medians from before and after including the outlier.
```{r}
mean(with_outlier) - mean(without_outlier)
median(with_outlier) - median(without_outlier)
```


7. Make at least two observations about the results (your new graphs) in an unordered list.
* The median's of the two are very close to each other.
* The graph appears to be skewed.

8. Finally, `knit` your work as either an HTML or PDF document, and upload that document back into the CatCourses assignment.