---
title: "Exploration 1"
author: "Kenneth Martin"
date: "1/26/2020"
output: 
  html_document:
        theme: cerulean
---

# Math 32
## Exploration 1

In this `exploration`, you are asked to

* simulate rolling two or three dice
* graph the results as histograms

1. First,
    a. Type your name into the author field in the YAML parameters above
    b. Also save this file while replacing "template" with your full name (be sure to keep the *.rmd file format).

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```

```{r}
N  <- 10000 # Number of iterations
X1 <- sample(1:6, N, replace = TRUE) # Generate random sample init X1
X2 <- sample(1:6, N, replace = TRUE) # Generate random sample init X2

sums <- X1 + X2 # Store into sums

df <- data.frame(sums) # Create dataframe for sums

ggplot(df, aes(x = sums)) +
  geom_histogram(binwidth = 1, color = "black", fill = "white") +
  labs(title = "Two Dice",
       subtitle = "Simulation of dice rolls",
       caption = "Math 32") +
  scale_x_continuous(name = "total", breaks = 2:12)
```

2. Demonstrate your understanding about the above example code block above by adding at least 5 comments in your own words.

3. Make at least two observations about the results (the graph) in an unordered list.
    * The graph is normal and does not skew to one side.
    * Numbers on the smaller end and the larger end have been rolled less because the probabilty of rolling a 1 or a 12 is a lot smaller than rolling a 7.
    
4. Now let us try a more complicated setting.  In a new code block,
    * simulate rolling *three* dice at a time
    * run the simulation for at least 20,000 iterations
    * change the $x$-axis tick marks since the sample space is now $\{3, 4, ..., 18\}$
    * change the color that is *inside* of the rectangles
    * replace "Math 32" with your name in the caption
```{r}
N <- 20000 # Sample Size

X1 <- sample(1:6, N, replace = TRUE) # Generate random sample init X1
X2 <- sample(1:6, N, replace = TRUE) # Generate random sample init X2
X3 <- sample(1:6, N, replace = TRUE) # Generate random sample init X3

sums <- X1 + X2 + X3  # Store into sums

df <- data.frame(sums) # Create dataframe for sums

ggplot(df, aes(x = sums)) +
  geom_histogram(binwidth = 1, color = "black", fill = "navy blue") +
  labs(title = "Three Dice",
       subtitle = "Simulation of dice rolls",
       caption = "Kenneth Martin") +
  scale_x_continuous(name = "total", breaks = 3:18)
```
    
    
5. Make at least two observations about your new results (the graph) in an unordered list.
    * I noticed a larger gap between the middle values (10-11) and the outer values (3 and 18).
    * As we increased the sample size there were more values to sample from, so the curve is much more distinguishable. 

6. Finally, `knit` your work as either an HTML or PDF document, and upload that document back into the CatCourses assignment.